Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
montecarlo aws

\subsubsection{GPUs}
As it has been said before, an instance is based in a VM 
which is running on a real node with its own virtualized 
components, so it is possible that AWS could use a virtualization 
framework to offer GPU services to all the instances.
Therefore, we need to verify if the GPUs showed in the instances are 
non-virtualized GPUs so, we have executed the NVIDIA SDK test called 
bandwidthtest. As it is shown in the Table~\ref{table:bwt}, as the bandwidth achieved 
in this test is higher than the network bandwith, it reveals that it is a 
real GPU. 
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK bandwidthtest execution transfering 32MB using pageable memory }
\label{table:bwt}
\tabcolsep=0.05cm
\begin{center}\begin{tabular}{cccc}
Name &  Data Movement & Network & BandWidth (MB/s)\\ \hline \hline
g2.2xlarge & Host to Device & Hight& 3,004.5\\ \hline
g2.2xlarge & Device to Host & Hight& 2,809.2\\ \hline
g2.8xlarge & Host to Device & 10 Gb& 2,814.7\\ \hline
g2.8xlarge & Device to Host & 10 Gb& 3,182.3\\ \hline
\end{tabular}\end{center}\end{table}

\subsection{Testbed Scenarios}
\begin{figure*}[ht]
\centering
\subfigure[5 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{Different scenario configurations where an AWS instance acting as a client is using several remote GPUs}
\label{fig:aws}
\end{figure*}

\subsection{Experiments}
\subsection{Results}
Flexibility and economical expenses

\section{GPGPU Shared Service in OpenStack}
In this section is explained all the work related to OpenStack that has been done, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

@@

\section*{\uppercase{Acknowledgements}}
The researchers from the Universidad Jaume~I were supported by Universitat Jaume I research project (P11B2013-21), project
TIN2011-23283 and~FEDER.

>>>>

\subsubsection{GPUs}
As it has been said before, an instance is based in a VM 
which is running on a real node with its own virtualized 
components, so it is possible that AWS could use a virtualization 
framework to offer GPU services to all the instances.
Therefore, we need to verify if the GPUs showed in the instances are 
non-virtualized GPUs so, we have executed the NVIDIA SDK test called 
bandwidthtest. As it is shown in the Table~\ref{}, as the bandwidth achieved 
in this test is higher than the network bandwith, it reveals that it is a 
real GPU.

\subsection{Testbed Scenarios}
\begin{figure*}[!t]
\centering
\subfigure[5 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{Different configurations where an AWS instance acting as a client is using several remote GPUs}
\label{fig:aws}
\end{figure*}

\subsection{Experiments}
\subsection{Results}

\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont2.png}
  \caption{Montecarlo execution time}
  \label{fig:internal}
\end{figure}
\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{Montecarlo options per second}
  \label{fig:internal}
\end{figure}

Flexibility and economical expenses

\section{GPGPU Shared Service in OpenStack}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

@@

\section*{\uppercase{Acknowledgements}}
The authors would like to thank the IT members of the department Vicente Roca and Gustavo Edo for their help.

The researchers were supported by Universitat Jaume I research project (P11B2013-21), project
TIN2011-23283 and~FEDER.
